Pool Model

### 2025-08-28 pool_model.tex
add more notes

How well does the pool model do to encapsulate all the different growth models
\begin{itemize}
    \item All 6 models can be represented by pool model
    \item Baranyi-Roberts results can be reproduced, but not identical; requires some work
    \item what are some general limitations within this framework? how can they be circumvented?
\end{itemize}

@@

% ------------------------------------------------------------------------------------------------
\section{Conclusion}
\newpage
\printbibliography

@@

>>>>

How well does the pool model do to encapsulate all the different growth models
\begin{itemize}
    \item All 6 models can be represented by pool model
    \item Baranyi-Roberts results can be reproduced, but not identical; requires some work
    \item what are some general limitations within this framework? how can they be circumvented?
    \item why is the pool model "better" than the other \ac{ode} models? (why did we do this?);
        generalization of many models; better explainability;
    \item link to supplement; we can generalize this and prove theorems for the abstract,
        generalized model; this allows us to discuss many cases at once
\end{itemize}

@@

% ------------------------------------------------------------------------------------------------
\section{Conclusion}
\noindent
\begin{itemize}
    \item New theoretical framework
    \item consistent with \ac{ode} models (Baranyi-Roberts)
    \item Better explainability
    \item Include effects such as inhibition, toxins in understandable manner
    \item showed spatial limitations of \ac{ode} model
    \item \ac{abm} model allowed modeling of cellular processes; ensure that pool model is derivable
        from the individual behvaiour of cellular processes
\end{itemize}

\newpage
\printbibliography

@@

\textbf{!Christian extend this!}
